
```{r}
library(tidyverse) 
library(ggplot2)
library(readr)

df<-read.csv("Automobile_data.csv", header = TRUE)
str(df)
```


```{r}
# Check how many '?' entries in each column
colSums(df == '?')
```

```{r}
# Check how many "?" entries by row
table(rowSums(df == "?"))
```

```{r}
# Check for missing values
sapply(df, function(x) sum(is.na(x)))
```

Data Cleaning

```{r}
# Firstly, let's take a look at "num.of.doors" variable, since it is a categorial variable
levels(df$num.of.doors) 
df %>% filter(num.of.doors == "?") %>% select(make, body.style)
table(df$make,df$num.of.doors)
table(df$body.style,df$num.of.doors)
```

```{r}
# Plot body style vs number of doors (colours: vehicle make)
ggplot(df, aes(num.of.doors, body.style)) + geom_jitter(aes(color=make), size = 3) + labs(title = "All vehicle makes") # all data
ggplot(filter(df,make=="mazda" | make=="dodge"), aes(num.of.doors, body.style)) + geom_jitter(aes(color=make), size = 3) + labs(title = "Mazda, Dodge") 
```

It seems that most sedans are four doors across the brands, especially for Mazda and Dodge. Let's assign the 4 to the "?" entries for number of doors

```{r}
df$num.of.doors[df$num.of.doors == "?"] <- "four"
```

Now, let's take a look at the remaining variables with "?" entries. Let's'set these entries to "NA"

```{r}
df$bore[df$bore == "?"] <- NA
df$stroke[df$stroke == "?"] <- NA
df$horsepower[df$horsepower == "?"] <- NA
df$peak.rpm[df$peak.rpm == "?"] <- NA
df$price[df$price == "?"] <- NA
df$normalized.losses[df$normalized.losses == "?"] <- NA

#convert to numerics

df$bore<-as.numeric(as.character(df$bore))
df$stroke<-as.numeric(as.character(df$stroke))
df$horsepower<-as.numeric(as.character(df$horsepower))
df$peak.rpm<-as.numeric(as.character(df$peak.rpm))
df$price<-as.numeric(as.character(df$price))
df$normalized.losses<-as.numeric(as.character(df$normalized.losses))
```

MICE (Multivariate Imputation via Chained Equations)

The mice package in R helps to impute missing values with plausible data values. The mice package provides a function md.pattern() to get a better understanding of the pattern of the missing data The mice() function takes care of the imputing process

```{r}
library(mice)

# Remove categorial variables
df.num <- df[sapply(df, is.numeric)]
md.pattern(df.num)
tempData <- mice(df.num,m=1,maxit=5,meth='pmm',seed=500)
summary(tempData)

# m  – Refers to 5 imputed data sets
# maxit – Refers to no. of iterations taken to impute missing values
# method – Refers to method used in imputation. pmm refers to predictive mean matching and is used for numerical variables
```


```{r}
# To check imputed values
tempData$imp$horsepower
tempData$imp$stroke
tempData$imp$bore
tempData$imp$peak.rpm
tempData$imp$normalized.losses
```


```{r}
# Plot of variables (scatter plot)
xyplot(tempData, horsepower ~ stroke + bore + peak.rpm,pch=18,cex=1)
```

```{r}
df.num <- complete(tempData,1)

df.non_num <- df[, -which(names(df) %in% names(df.num))]
df <- cbind(df.num, df.non_num)

# Final check on missing entries
sapply(df, function(x) sum(is.na(x)))
sapply(df, function(x) sum(df == "?"))
```

data Visualisation: Numerical Data
```{r}

```

```{r}
# 1. To visualise the relationship between price and car specifications
# Scatter plot
df.num %>% select(-c(symboling)) %>%
    gather(-price, key = "var", value = "Specifications") %>%
    ggplot(aes(x = price, y = Specifications)) +
    geom_point() +
    facet_wrap(~ var, scales = "free") +
    ggtitle('Relationship between Price & Specifications')

# Correlation matrix with colours
library(corrplot)
df.num %>% select(-c(symboling,normalized.losses)) %>% as.matrix() %>% cor() %>% corrplot(method = "number")
```

Data Visualization: Categorial Data

1.Car make

```{r}
# Car Make (car company)
df %>% group_by(make) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(make,count),y=count)) + geom_bar(stat = "identity") + coord_flip() +
    xlab("Car Make") + ylab("Count")

# Boxplot
df %>% select(make,price) %>%  ggplot(aes(x= make,y=price)) + geom_boxplot() + coord_flip() +  xlab("Car Make") + ylab("Price")
```

2. Fuel Type

The average price of a diesel car is higher than that of gas cars. This may explain why more gas cars were sold as compared to diesel cars.

```{r}
# Fuel type
df %>% group_by(fuel.type) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(fuel.type,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Fuel type") + ylab("Count")

# Boxplot
df %>% select(fuel.type,price) %>%  ggplot(aes(x= fuel.type,y=price)) + geom_boxplot() +  xlab("Fuel Type") + ylab("Price")
```

3. Aspiration

The average price of cars with turbo aspiration is higher than that of standard aspiration. This may explain why more cars with standard aspiration were sold as compared to cars with turbo aspiration

```{r}
# Aspiration
df %>% group_by(aspiration) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(aspiration,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Aspiration") + ylab("Count")

# Boxplot
df %>% select(aspiration,price) %>%  ggplot(aes(x= aspiration,y=price)) + geom_boxplot() +  xlab("Aspiration") + ylab("Price")
```

4. Engine Location

```{r}
# Engine Location
df %>% group_by(engine.location) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(engine.location,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Engine Location") + ylab("Count")

# Boxplot
df %>% select(engine.location,price) %>%  ggplot(aes(x= engine.location,y=price)) + geom_boxplot() +  xlab("Engine Location") + ylab("Price")
```

5. Engine Type
```{r}
# Engine Type
df %>% group_by(engine.type) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(engine.type,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Engine Type") + ylab("Count")

# Boxplot
df %>% select(engine.type,price) %>%  ggplot(aes(x= engine.type,y=price)) + geom_boxplot() +  xlab("Engine Type") + ylab("Price")
```


6. Fuel System
```{r}
# Fuel System
df %>% group_by(fuel.system) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(fuel.system,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Fuel System") + ylab("Count")

# Boxplot
df %>% select(fuel.system,price) %>%  ggplot(aes(x= fuel.system,y=price)) + geom_boxplot() +  xlab("Fuel System") + ylab("Price")
```


7. Body Style

```{r}
# Body Style
df %>% group_by(body.style) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(body.style,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Body Style") + ylab("Count")

# Boxplot
df %>% select(body.style,price) %>%  ggplot(aes(x= body.style,y=price)) + geom_boxplot() +  xlab("Body Style") + ylab("Price")
```


8. Drive wheels
```{r}
# Drive wheels
df %>% group_by(drive.wheels) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(drive.wheels,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Drive Wheels") + ylab("Count")

# Boxplot
df %>% select(drive.wheels,price) %>%  ggplot(aes(x= drive.wheels,y=price)) + geom_boxplot() +  xlab("Drive Wheels") + ylab("Price")
```

9. Number of cylinders

```{r}
# Num of cylinders
df %>% group_by(num.of.cylinders) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(num.of.cylinders,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Num of cylinders") + ylab("Count")

# Boxplot
df %>% select(num.of.cylinders,price) %>%  ggplot(aes(x= num.of.cylinders,y=price)) + geom_boxplot() +  xlab("Num of cylinders") + ylab("Price")
```


9. Symboling

```{r}
# Symboling
df %>% group_by(symboling) %>% summarise(count = n()) %>%  
    ggplot(aes(x= reorder(symboling,count),y=count)) + geom_bar(stat = "identity") +
    xlab("Symboling") + ylab("Count")

# Boxplot
df %>% select(symboling,price) %>% ggplot(aes(x= symboling,y=price)) + geom_boxplot() +  xlab("Symboling") + ylab("Price")
```

